---
title: "Data Merging, Visuals, and Analysis - Abigail Sikora"
output: html_document
date: "2023-11-01"
---

Below is the code to filter the Trips_by_Distance csv to only contain data from Nashville, Tennesse.
```{r}
library(tidyverse)
#read in data set
trips<-read_csv("Trips_by_Distance.csv")

#filter to only have data from Tennessee
TN<-subset(trips, trips$`State FIPS`=="47")

#filter to only have data from Davidson County (where Nashville is)
davidson_county<-subset(TN,TN$`County Name`=="Davidson County")

#export to csv
write_csv(davidson_county,"Trips_by_davidsoncounty.csv")
```

Below is filtered/reading in the business.json file to contain information on bars/nightlife categories of businesses in Nashville.
```{r}
library(jsonlite)
json_file_path_within_zip <- "yelp_Fall2023/business.json"

# Read the JSON data from the zip archive
business <- jsonlite::stream_in(unz("yelp_Fall2023.zip", json_file_path_within_zip))
nashville<-subset(business, city=="Nashville")

#only pick the data rows that contain "Bars" or "Nightlife" in categories listed
nashville_bars<-nashville[grepl("Bars|Nightlife", nashville$categories),]


#export filtered data to json file
write_json(nashville_bars,"nashville_bars_nightlife.json")
```


```{r}
json_file_path_within_zip <- "yelp_Fall2023/review.json"

# Initialize an empty dataframe to store combined filtered results
combined_filtered_data <- data.frame()

#filter function to only get reviews from Nashville bars/nightlife businesses
filter_function <- function(data) {
  max_records <- Inf 

  if (nrow(combined_filtered_data) < max_records) {
    # Filter the data based on whether "business_id" is in nashville_bars
    filtered_data <- data[data$business_id %in% nashville_bars$business_id, ]
    combined_filtered_data <<- rbind(combined_filtered_data, filtered_data)
  }

  return(data)  # Return the original data to keep reading more records
}

json_stream <- jsonlite::stream_in(unz("yelp_Fall2023.zip", json_file_path_within_zip), handler = filter_function)

#export filtered data to json file
write_json(combined_filtered_data, "filtered_reviews.json")
```
ggplot(review_data, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Number of Reviews by Stars"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
Next is the code used for some of the visuals in the first presentation. This includes the visuals shown on slides 3-4.
```{r}
dancedf <- reviews[grepl("dance|dancing", reviews$text, ignore.case = TRUE), ]
ggplot(dancedf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Dancing"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
```{r}
cocktailsdf <- reviews[grepl("cocktails", reviews$text, ignore.case = TRUE), ]
ggplot(cocktailsdf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Cocktails"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
```{r}
musicdf <- reviews[grepl("music", reviews$text, ignore.case = TRUE), ]
ggplot(musicdf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Music"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
```{r}
peopledf <- reviews[grepl("people", reviews$text, ignore.case = TRUE), ]
ggplot(peopledf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="People"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
