---
title: "Data Merging, Visuals, and Analysis - Abigail Sikora"
output: html_document
date: "2023-11-01"
---

Below is the code to filter the Trips_by_Distance csv to only contain data from Nashville, Tennesse.
```{r}
library(tidyverse)
#read in data set
trips<-read_csv("Trips_by_Distance.csv")

#filter to only have data from Tennessee
TN<-subset(trips, trips$`State FIPS`=="47")

#filter to only have data from Davidson County (where Nashville is)
davidson_county<-subset(TN,TN$`County Name`=="Davidson County")

#export to csv
write_csv(davidson_county,"Trips_by_davidsoncounty.csv")
```

Below is filtered/reading in the business.json file to contain information on bars/nightlife categories of businesses in Nashville.
```{r}
library(jsonlite)
json_file_path_within_zip <- "yelp_Fall2023/business.json"

# Read the JSON data from the zip archive
business <- jsonlite::stream_in(unz("yelp_Fall2023.zip", json_file_path_within_zip))
nashville<-subset(business, city=="Nashville")

#only pick the data rows that contain "Bars" or "Nightlife" in categories listed
nashville_bars<-nashville[grepl("Bars|Nightlife", nashville$categories),]


#export filtered data to json file
write_json(nashville_bars,"nashville_bars_nightlife.json")
```


```{r}
json_file_path_within_zip <- "yelp_Fall2023/review.json"

# Initialize an empty dataframe to store combined filtered results
combined_filtered_data <- data.frame()

#filter function to only get reviews from Nashville bars/nightlife businesses
filter_function <- function(data) {
  max_records <- Inf 

  if (nrow(combined_filtered_data) < max_records) {
    # Filter the data based on whether "business_id" is in nashville_bars
    filtered_data <- data[data$business_id %in% nashville_bars$business_id, ]
    combined_filtered_data <<- rbind(combined_filtered_data, filtered_data)
  }

  return(data)  # Return the original data to keep reading more records
}

json_stream <- jsonlite::stream_in(unz("yelp_Fall2023.zip", json_file_path_within_zip), handler = filter_function)

#export filtered data to json file
write_json(combined_filtered_data, "filtered_reviews.json")
```
ggplot(review_data, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Number of Reviews by Stars"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
Next is the code used for some of the visuals in the first presentation. This includes the visuals shown on slides 3-4.
```{r}
dancedf <- reviews[grepl("dance|dancing", reviews$text, ignore.case = TRUE), ]
ggplot(dancedf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Dancing"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
```{r}
cocktailsdf <- reviews[grepl("cocktails", reviews$text, ignore.case = TRUE), ]
ggplot(cocktailsdf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Cocktails"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
```{r}
musicdf <- reviews[grepl("music", reviews$text, ignore.case = TRUE), ]
ggplot(musicdf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="Music"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
```{r}
peopledf <- reviews[grepl("people", reviews$text, ignore.case = TRUE), ]
ggplot(peopledf, aes(x=stars))+
  geom_bar(fill="dodgerblue")+
  labs(
    x="Stars",
    y="Number of Reviews",
    title="People"
  )+
  theme_minimal()+
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    plot.title=element_text(size=16, hjust=0.5)
  )
```
Next is the code used for further analysis as seen in presentation 2. This includes the two sample t-tests.
```{r}
#data clean up and changing data types
business_normalized <-business %>%
  mutate(normalized_stars = weighted.mean(stars, w=review_count,na.rm=TRUE))
head(business)
head(business$attributes)
business$postal_code<-as.factor(business$postal_code)
business$attributes$HappyHour<-as.factor(business$attributes$HappyHour)
business$attributes$OutdoorSeating<-as.factor(business$attributes$OutdoorSeating)
business$attributes$NoiseLevel<-as.factor(business$attributes$NoiseLevel)
business$attributes$Smoking<-as.factor(business$attributes$Smoking)
summary(business$attributes)
business$stars<-as.numeric(business$stars)


#two sample t-test: analysis on happy hour
t1 <- t.test(normalized_stars ~ attributes$HappyHour, data=business, var.equal=FALSE)
t1

#anova test on location
t2 <- aov(normalized_stars ~ postal_code, data=business)
summary(t2)
tukey_result<-as.data.frame(TukeyHSD(t2))

significant_pairs <- subset(tukey_result, abs(diff) > 1)

# Print the filtered results
print(significant_pairs)




tukey_result <- TukeyHSD(t2)

# Print the Tukey HSD results
print(tukey_result)
model <- lm(business$stars ~ business$attributes$HappyHour + business$postal_code)
summary(model)
```
